---
title: "June - C1 - SAF validations report"
date: "`r Sys.Date()`"
sgtemplates:
  datatables:
    features:
      info: true
      ordering: true
      paging: true
      searching: false
  header:
    phase_banner:
      tag: "WIP"
      text: "This is a work in progress."
    site_branding: "Scottish Government"
  metadata:
    label: "Report"
  navigation:
    toc:
      sticky: false
output:
  html_document:
    code_download: false
    df_print: paged
    fig_caption: true
    number_sections: false
    self_contained: false
    template: "_template.html"
    toc: true
    toc_depth: 2
    toc_float: false
---
```{r setup , include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      fig.align = "center",
                      fig.width = 4, 
                      fig.height = 4, 
                      dev = "png",
                      cache = TRUE,
                      warning = FALSE, 
                      message = FALSE)

# Load packages

library(tidyverse)
library(knitr)
library(writexl)
library(RtoSQLServer)

#Script containing datasets and validations
source("June - C1 - SAF validations.R",  local = knitr::knit_global())

```

# SAF Validations

# Section 1 Flagged holdings

## Flag 1
The following table displays errors for flag1: Field ID (FID) recorded as belonging to multiple holdings (Single Location Code: SLC) on permanent sheets where one reported it as seasonally let out (LLO). A permanent tenancy may incorrectly be recorded as a seasonal let out]'/


```{r, results = 'markup'}

ifelse(nrow(flaggedholdings_flag1) ==0, "No errors found", "Errors found)")

kable(flaggedholdings_flag1 , caption = "Flag 1")


```
##  Flag 2 
Duplicate lines, and in the total recorded land use area to be'/substantially greater than the recorded field area'/[May be a data entry error]'/

```{r, results = 'markup'}

ifelse(nrow(flaggedholdings_flag2) ==0, "No errors found", "Errors found)")

kable(flaggedholdings_flag2 , caption = "Flag 2")


```
## Flag 3
Land reported as LLO, and total recorded land use area to be'/substantially greater than the recorded field area'/[May be a seasonal tenancy incorrectly entered on permanent sheet]'/


```{r, results = 'markup'}

ifelse(nrow(flaggedholdings_flag3) ==0, "No errors found", "Errors found)")

kable(flaggedholdings_flag3 , caption = "Flag 3")


```
## Flag 4
On seasonal sheet, MLC and SLC are identical'/[May be a permanent tenancy incorrectly entered on seasonal sheet]'/


```{r, results = 'markup'}

ifelse(nrow(flaggedholdings_flag4) ==0, "No errors found", "Errors found)")

kable(flaggedholdings_flag4 , caption = "Flag 4")


```
## Flag 5
The total recorded land use area is greater than the recorded'/field area by a factor of 10 or 100'/[May be a decimal place error]'/

```{r, results = 'markup'}

ifelse(nrow(flaggedholdings_flag5) ==0, "No errors found", "Errors found)")

kable(flaggedholdings_flag5 , caption = "Flag 5")


```
## Flag 6
SLC = 000/0000 on permanent land or MLC = 000/000 on seasonal land'/		- ie. parish/holding is unknown'/

```{r, results = 'markup'}

ifelse(nrow(flaggedholdings_flag6) ==0, "No errors found", "Errors found)")

kable(flaggedholdings_flag6, caption = "Flag 6")


```
## Flag 7
FID recorded as belonging to multiple holdings (SLC) without any reported as seasonally let out (LLO).

```{r, results = 'markup'}

ifelse(nrow(flaggedholdings_flag7) ==0, "No errors found", "Errors found)")

kable(flaggedholdings_flag7 , caption = "Flag 7")


```
## Flag 8 

Other land where total recorded land use area is substantially'/   greater than the recorded field area'/

```{r, results = 'markup'}

ifelse(nrow(flaggedholdings_flag8) ==0, "No errors found", "Errors found)")

kable(flaggedholdings_flag8, caption = "Flag 8")


```

 ## Flag 9

EXCL land where total recorded land use area is substantially'/ greater than the recorded field area'/
```{r, results = 'markup'}

ifelse(nrow(flaggedholdings_flag9) ==0, "No errors found", "Errors found)")

kable(flaggedholdings_flag9 , caption = "Flag9")


```

# Section 2 Automatic corrections made


