---
title: "JAC Punch Error Check (C1)"
date: "`r Sys.Date()`"
sgtemplates:
  datatables:
    features:
      info: true
      ordering: true
      paging: true
      searching: false
  header:
    phase_banner:
      tag: "WIP"
      text: "This is a work in progress."
    site_branding: "Scottish Government"
  metadata:
    label: "Report"
  navigation:
    toc:
      sticky: false
output:
  html_document:
    code_download: false
    df_print: paged
    fig_caption: true
    number_sections: false
    self_contained: false
    template: "_template.html"
    toc: true
    toc_depth: 2
    toc_float: false
---
```{r setup, include = FALSE } 
library(tidyverse)
library(knitr)
#yr = this year 20xx
yr <- 21
yr1 <- yr-1 
yr2 <-  yr-2
yr3 <-  yr-3
yr_list <- c(yr, yr1, yr2)

knitr::opts_chunk$set(echo = FALSE)



# Before import -----------------------------------------------------------


# Clear environment prior
rm (list=(ls()))

# Datashare file path for import and export

Code_directory <-
  ("//s0177a/datashare/seerad/ags/census/branch1/NewStructure/Surveys/June/Codeconversion_2023")

# ADM schema for export

server <- "s0196a\\ADM"
database <- "RuralAndEnvironmentalScienceFarmingStatistics"
schema <- "juneagriculturalsurvey2023alpha"

#Script containing datasets and error checks
source("./punch-error-checks_files/punch error tables.R",  local = knitr::knit_global())

```

# JAC Survey form Punch Error Checks
## Punch error 1
The following table displays errors for holdings where:  total area has gone up or down by 10% and there has been an increase of grass greater than 5 years in the last year that does not account for the total of last year's rough grazings, fallow, other land and the difference in total land use area change.

```{r, punch error tables-perr1, results = 'markup'}

perr1 <- perr1 %>% filter(error == "Error")  
  rename(perr1, yr = tillage, yr1 = otillage, yr2 =votillage)
  ifelse(nrow(perr1) ==0, "No errors found", "Errors found")
kable(perr1, caption = "Potential errors for tillage (tillage - item40 + item2321)" )


```

## Punch error 2
The following table displays possible errors for holdings where there is a large change in pigs

```{r, punch error tables-perr2, results = 'markup'} 
perr2 <- perr2 %>% filter(error == "Error") %>% 
  rename(yr = item157, yr1 = oitem157, yr2 =voitem157)
ifelse(nrow(perr2) ==0,  "No errors found", "Errors found")
kable(perr2, caption = "Potential errors for pigs (item157)" )

```

## Punch error 3
The following table displays possible errors for holdings where there are suspicious changes in total poultry numbers

```{r, punch error tables-perr3, results = 'markup'} 
perr3 <- perr3 %>% filter(error == "Error") %>% 
  rename(yr = item170, yr1 = oitem170, yr2 =voitem170)
ifelse(nrow(perr3) ==0,  "No errors found", "Errors found")
kable(perr3, caption = "Potential errors for total poultry (item170)" )

```

<!-- ## Punch error 4 -->
<!-- The following table displays possible errors for holdings where there are suspicious changes in total cattle numbers -->
<!-- ```{r, punch error tables-perr4, results = 'markup'}  -->
<!-- perr4 <- perr4 %>% filter(error == "Error") %>%  -->
<!--   rename(yr = cts312, yr1 = octs312, yr2 =vocts312) -->
<!-- ifelse(nrow(perr4) ==0,  "No errors found", "Errors found") -->
<!-- kable(perr4, caption = "Potential errors for total cattle (cts312)" ) -->
<!-- ``` -->

<!-- ## Punch error 5 -->
<!-- The following table displays possible errors for holdings where dairy has been introduced to a beef holding -->
<!-- ```{r, punch error tables-perr5, results = 'markup'}  -->
<!-- perr5 <- perr5 %>% filter(error == "Error") %>%  -->
<!--   rename(yr = dairy, yr1 = odairy, yr2 =vodairy) -->
<!-- ifelse(nrow(perr5) ==0,  "No errors found", "Errors found") -->
<!-- kable(perr5, caption = "Potential errors introduction of dairy to beef holding" ) -->

<!-- ``` -->

<!-- ## Punch error 6 -->
<!-- The following table displays possible errors for holdings where beef has been introduced to a dairy holding -->
<!-- ```{r, punch error tables-perr6, results = 'markup'}  -->
<!-- perr6 <- perr6 %>% filter(error == "Error") %>%  -->
<!--   rename(yr = beef, yr1 = obeef, yr2 =vobeef) -->
<!-- ifelse(nrow(perr3) ==0,  "No errors found", "Errors found") -->
<!-- kable(perr6, caption = "Potential introduction of beef to dairy holding" ) -->

<!-- ``` -->

## Punch error 7
The following table displays possible errors for holdings where there is a large change in total sheep numbers

```{r, punch error tables-perr7, results = 'markup'} 
perr7 <- perr7 %>% filter(error == "Error") %>% 
  rename(yr = item145, yr1 = oitem145, yr2 =voitem145)

ifelse(nrow(perr7) ==0,  "No errors found", "Errors found")
kable(perr7, caption = "Potential errors for total sheep (item145)" )

```

## Punch error 9
The following table displays possible errors for holdings where there is a large change in soft fruit area

```{r, punch error tables-perr9, results = 'markup'} 
perr9 <- perr9 %>% filter(error == "Error") %>% 
  rename(yr = item37, yr1 = oitem37, yr2 =voitem37)

ifelse(nrow(perr9) ==0,  "No errors found", "Errors found")
kable(perr9, caption = "Potential errors in soft fruit area (item37)" )

```

## Punch error 10
The following table displays possible errors for holdings where there is a large change in glasshouse area 

```{r, punch error tables-perr 10, results = 'markup'} 
perr10 <- perr10 %>% filter(error == "Error") %>% 
  rename(yr = glass, yr1 = oglass, yr2 =voglass)
ifelse(nrow(perr10) ==0,  "No errors found", "Errors found")
kable(perr10, caption = "Potential errors in glasshouse area" )

```

<!-- ##Punch error 11 -->
<!-- The following table displays possible errors for holdings where there has been an introduction of male cattle to holding with only female cattle (excluding bulls for service) -->
<!-- ```{r, punch error tables-perr11, results = 'markup'}  -->
<!-- perr11 <- perr11 %>% filter(error == "Error") %>%  -->
<!--   rename(yr = male, yr1 = omale, yr2 =vomale) -->
<!-- ifelse(nrow(perr10) ==0,  "No errors found", "Errors found") -->
<!-- kable(perr11, caption = "Potential introduction of male cattle to holding with only female cattle (excluding bulls for service)" ) -->

<!-- ``` -->
<!-- ##Punch error 12 -->
<!-- The following table displays possible errors for holdings where there has been an introduction of female cattle (not for breeding) to holding with only male cattle' -->
<!-- ```{r, punch error tables-perr12, results = 'markup'}  -->
<!-- perr12 <- perr12 %>% filter(error == "Error") %>%  -->
<!--   rename(yr = female, yr1 = ofemale, yr2 =vofemale) -->
<!-- ifelse(nrow(perr10) ==0,  "No errors found", "Errors found") -->
<!-- kable(perr12, caption = "Potential introduction of female cattle (not for breeding) to holding with only male cattle" ) -->

<!-- ``` -->

## Punch error 13
The following table displays possible errors for holdings where there has been a switch from ware to seed potatoes

```{r, punch error tables-perr13, results = 'markup'} 
perr13 <- perr13 %>% filter(error == "Error") %>% 
  rename(yr = ware, yr1 = oware, yr2 =voware)

ifelse(nrow(perr13) ==0,  "No errors found", "Errors found")
kable(perr13, caption = "Potential errors for switch from ware to seed potatoes" )

```
## Punch error 14
The following table displays possible errors for holdings where there is a large shift in deer numbers or movement from zero or to zero

```{r, punch error tables-perr14, results = 'markup'} 
perr14 <- perr14 %>% filter(error == "Error") %>% 
  rename(yr = item94, yr1 = oitem94, yr2 =voitem94)
ifelse(nrow(perr14) ==0,  "No errors found", "Errors found")
kable(perr14, caption = "Potential errors for large shift in deer numbers or movement from zero or to zero (item94)" )

```
## Punch error 15
The following table displays possible errors for holdings where there is a large change in total land area

```{r, punch error tables-perr15, results = 'markup'} 
perr15 <- perr15 %>% filter(error == "Error") %>% 
  rename(yr = item50, yr1 = oitem50, yr2 =voitem50)
ifelse(nrow(perr15) ==0,  "No errors found", "Errors found")
kable(perr15, caption = "Potential errors for large change in total land area (item50)" )

```
## Punch error 16
The following table displays possible errors for holdings where there is a large change in rough grazing area
```{r, punch error tables-perr16, results = 'markup'} 
perr16 <- perr16 %>% filter(error == "Error") %>% 
  rename(yr = item47, yr1 = oitem47, yr2 =voitem47)
ifelse(nrow(perr16) ==0,  "No errors found", "Errors found")
kable(perr16, caption = "Potential errors for large change in rough grazing area (item47)" )

```
<!-- ##Punch error 17 -->
<!-- The following table displays possible errors for holdings where there is a large change in migrant labour -->
<!-- ```{r, punch error tables-perr17, results = 'markup'}  -->
<!-- perr17 <- perr17 %>% filter(error == "Error") %>%  -->
<!--   rename(yr = item2511, yr1 = oitem2511, yr2 =voitem2511) -->
<!-- ifelse(nrow(perr17) ==0,  "No errors found", "Errors found") -->
<!-- kable(perr17, caption = "Potential errors for large change in migrant labour (item2511)" ) -->

<!-- ``` -->
# Punch error summary table 
The following table displays the count of punch errors grouped by "survtype". The count of observations per survtype is given.
```{r, punch error tables-perr-summary, results = 'markup'} 

kable(punch_error_summary, caption = "Count of punch errors by survtype (observations of survtype given in Count column)")

```

